\documentclass[11pt]{article}

% This is a tex file to make Alexander Mikheyev's CV.
% The content is

\usepackage[utf8]{inputenc}

\usepackage{rz-vita}
%\usepackage[english]{isodate}
%\printdayoff\numdate
\def\printdate#1{\xprintdate#1-}
\def\xprintdate#1-#2-#3-{#1}
\def\daterange#1#2{\xprintdate#1---\xprintdate#2-}

% Your biblatex file is likely somewhere else.
\addbibresource{mikheyev.bib}


\title{}
\name{Sasha (Alexander) S. Mikheyev}
% I guess postnoms is like junior? I dunno.
\postnoms{}
\address{
  Australian National University\\
  Research School of Biology\\
  Divisin of Ecology and Evolution\\
  RN Roberson Building\\
  46 Sullivans Creek Rd.\\
  Acton, ACT 2601\\
  Australia\\
}
\www{homologo.us}
\email{sasha@homologo.us}
\tel{+61 (0) 490 485 469}
\twitter{amikheyev}
\orcid{0000--0003-4369--1019}
\github{mikheyev}
\googlescholar{d1Q6iL0AAAAJ}
\subject{}


\begin{document}

\maketitle

\section{Education}

\ind PhD, \textbf{University of Texas, Austin}, Integrative Biology, \printdate{2009-05-01}


\ind MA, \textbf{University of Florida, Tallahassee}, Biology, \printdate{2002-05-01}


\ind B.A., \textbf{Cornell University}, Neurobiology and Behavior, \printdate{2000-05-01}



\section{Appointments}

\subsection{Australian National University, Research School of Biology}
\ind Senior Lecturer. \printdate{2018-06-01}--.

\ind Group Leader (Future Fellow). \printdate{2017-07-30}--.

\ind Associate Dean (International). \printdate{2019-00-00}--.

\subsection{Okinawa Institute of Science and Technology}
\ind Associate Professor (adjunct). \printdate{2017-00-00}--.

\ind Associate Professor. \daterange{2015-00-00}{2017-00-00}.

\ind Assistant Professor. \daterange{2012-00-00}{2015-00-00}.

\ind Independent New Investigator. \daterange{2009-08-00}{2012-00-00}.


\section{Academic awards}

\ind \textit{Future Fellowship (level 2)}, Australian Research Council, 2016--2020.

\ind \textit{\href{https://news.utexas.edu/2008/05/29/graduate-students-honored-for-excellence}{George H. Mitchell Award for Excellence in Graduate Research}}, University of Texas, 2008, (the university's top graduate research award).

\ind \textit{\href{http://iussi.cyberbee.net/wp-content/uploads/2010/04/2007\_Fall\_NAS-IUSSI\_Newsletter.pdf}{George Eickwort Award}}, North American Section of the International Union for the Study of
Social Insects, 2007, (for ``exceptional research and scholarly activity by students in the
field of social insect biology'').


\section{Editor}

\ind \textit{\href{https://mc.manuscriptcentral.com/jte}{Journal of Tropical Ecology}}, Editor-in-Chief. \printdate{2019-07-01}--.

\ind \textit{\href{http://openlogicproject.org/}{Myrmecological News}}, Subject Editor. \printdate{2013-00-00}--.

\ind \textit{\href{https://peerj.com/sasha/}{PeerJ}}, Academic Editor. \printdate{2015-00-00}--.


\section{Research Grants \& Fellowships}

\subsection{Grants}
\ind \textit{Australian National University}, Vice-Chancellor's Teaching Enhancement Grant, ``Teaching quantitative skills to biologists using an interactive virtual
environment''.  AU\$ \$9,989. 2019 (Project Lead, Co-applicants: Robert Lanfear, Teresa Neeman, Dan Noble
and Eric Stone).


\ind \textit{Ministry of Education, Culture, Sports, Science \& Technology in Japan}, KAKENHI Fund for the Promotion of Joint International Research, ``Using machine vision to understand causes and consequences of collective
behavior in a honey bee society''.  ¥13,130,000. 2016.



\ind \textit{Australian Research Council}, Discovery Project, ``Resolving the role of DNA methylation in insect social evolution''.  AU\$ 380,000. 2018 (Co-investigator with Luke Holman).


\ind \textit{Ministry of Education, Culture, Sports, Science \& Technology in Japan}, KAKENHI Grant-in-Aid for Scientific Research (B), ``Origins, spread and evolution of novel honey bee parasites and diseases''.  ¥16,900,000. 2018.


\ind \textit{Ministry of Education, Culture, Sports, Science \& Technology in Japan}, KAKENHI Young Scientist (A), ``Genetic control of honeybee dance''.  ¥16,640,000. 2016.


\ind \textit{Ministry of Education, Culture, Sports, Science \& Technology in Japan}, KAKENHI (S), ``Royal Epigenetics: Molecular basis of the extended longevity of
reproductives in social insects''.  ¥212,940,000. 2013 (co-PI with Kenji Matsuura (lead), Iuchi Yoshihito and Masaki Kamakura).


\ind \textit{Ministry of Education, Culture, Sports, Science \& Technology in Japan}, KAKENHI Young Scientist (B), ``Study of sex determination mechanisms in \textit{Wasmannia auropunctata}''.  ¥1,430,000. 2013.


\ind \textit{United States National Science Foundation}, Division Of Environmental Biology, ``Phylogenetic research on the origin and evolution of agriculture in ants''.  \$444,988.00. 2010 (Co-Pi with Ted Schultz (Principal Investigator), Charles Mitter, Ulrich
Mueller and Natasha Mehdiabadi).






\subsection{Fellowships}


\ind \textit{Australian Research Council}, Future Fellowship, ``The origins, global spread and evolution of novel honey bee parasites''.  AU\$ 809,000. 2018.








\ind \textit{U.S. Natinal Science Foundation}, Postdoctoral fellowship in biological informatics (\textit{declined}), ``Massive horizontal gene transfer in bdelloid rotifers: gathering junk or
evolutionary innovation?''.  2009 (A total of 15 fellowships per year are awarded country-wide. Declined in
order to take up an independent position in Japan.).


\ind \textit{Fulbright Foundation}, Fellowship to Cameroon and Gabon, ``Impact of an invasive ant on mainland Africa''.  2005--2006 (This fellowship has a \textasciitilde{}15\% funding rate to Sub-Saharan
Africa).


\ind \textit{Environmental Protection Agency}, STAR pre-doctoral fellowship, ``Worldwide traffic, impact and the evolutionary trajectory of invasive
populations in the little fire ant \textit{Wasmannia auropunctata}''.  2004--2005 (Median grant application award rate of 16\% in 2003--2014).



\section{Teaching}

\subsection{Australian National University}
\ind Ecology (BIOL2131), lecturer, 2019. (undergad).

\ind Evolution (BIOL2114), lecturer, 2017 -- 2019. (undergad).

\subsection{Okinawa Institute of Science and Technology Graduate University}
\ind Biology (B02), sole instructor, 2012 -- 2015. (grad).

\ind Quantitative Evolutionary Comparative Biology Workshop, organizer, 2011, 2012. (grad).

\subsection{University of Maryland University College}
\ind Introductory Biology Lab (BIOL 102), sole instructor, 2010. (undergrad).

\ind Introductory Biology (BIOL 101), sole instructor, 2010. (undergrad).

\subsection{Southwestern University}
\ind Genetics and Evolution (BIO50-122), sole instructor, 2007. (undergad).


\section{Students}

\subsection{Supervisor}
\ind Carmen Emborski (PhD), ``\href{https://ttu-ir.tdl.org/bitstream/handle/2346/74394/EMBORSKI-DISSERTATION-2018.pdf}{Transgenerational effects of ancestral dietary modifications:
investigations of progeny response consistency and modes of transmission},'' 2018

\ind Claire Morandin (PhD), ``\href{https://pdfs.semanticscholar.org/ce84/0a0475d80c276d36c4e6f6fa7a00d0f3524c.pdf}{To be or not to be a Queen -- Caste-specific gene expression patterns in
ants},'' 2015

\subsection{External Examiner}
\ind Thomas Dejaco (PhD, University of Innsbruck), ``Integrative species delimitation in the alpine jumping‐bristletail genus
\textit{Machilis latreille}, 1832,'' 2014

\subsection{Honours/Masters Committee Member}
\ind Holly Sargent (Honours, supervisor: Craig Moritz), ``Genetic erosion of island marsupial populations,'' 2018

\ind Somasundhari Shanmuganadam (Masters, supervisors: Benjamin Schwessinger /Robyn Hall), ``Uncovering the Hare microbiome,'' 2019


\section{Presentations}

\subsection{Invited Departmental Presentations}

\ind ``TBD.'' Viikki Lectures, University of Helsinki, Helsinki, Finland, \printdate{2020-00-00}.


\ind ``Coevolution while you wait: the arms race between honey bees and
ectoparasitic Varroa mites.'' Melbourne University School of BioSciences Seminar Series, Melbourne, Australia, \printdate{2019-00-00}.








\ind ``Using historical collections to understand the evolutionary response of
bees to an emergent parasite.'' Macquarie University, Sydney, Australia, \printdate{2016-00-00}.


\ind ``Evolutionary response by wild honey bees to \textit{Varroa}.'' Plymouth University, Plymouth, United Kigdom, \printdate{2016-00-00}.


\ind ``Evolutionary response by wild honey bees to \textit{Varroa}.'' Plymouth University, Plymouth, United Kigdom, \printdate{2016-00-00}.


\ind ``Evolutionary response by wild honey bees to \textit{Varroa}.'' Institute of Science and Technology, Vienna, Austria, \printdate{2016-00-00}.


\ind ``Evolutionary response by wild honey bees to \textit{Varroa}.'' Max Planck Institute for Evolutionary Biology, Plön, Germany, \printdate{2016-00-00}.


\ind ``Evolutionary response by wild honey bees to \textit{Varroa}.'' Texas A\&M University, College Station, Texas, United States, \printdate{2016-00-00}.


\ind ``Whole-genome re-sequencing of museum specimens reveals resilience to
disease in a feral population of European honey bees.'' Academia Sinica, Taipei, Taiwan, \printdate{2016-00-00}.


\ind ``Using historical collection to understand feral honey bee evolution.'' United States Department of Agriculture, Carl Hayden Bee Research Center, Tucson, Arizon, United States, \printdate{2015-00-00}.


\ind ``Using population genomics to look at selection and evolution in social
insects.'' University of Pennsylvania, Philadelphia, Pennsylvania, United States, \printdate{2015-00-00}.


\ind ``When subspecies collide: What can genome-wide signatures of
hybridisation tell us about speciation?.'' Australian National University, Species delimitation in the age of
genomics Workshop, Canberra, Australia, \printdate{2015-00-00}.


\ind ``Museum samples reveal population genomic changes associated with a rapid
evolutionary response by wild honey bees \textit{Apis mellifera} to a
novel parasite.'' Australian National University, Species delimitation in the age of
genomics Workshop, National University of Singapore Biology Colloquium, \printdate{2015-00-00}.


\ind ``Working with ancient DNA: tools and insights.'' Kzan' Federal University, Kazan', Russian Federation, \printdate{2014-00-00}.


\ind ``Working with degraded DNA: laboratory and bioinformatic approaches.'' CSIRO, Canberra, Australia, \printdate{2014-00-00}.


\ind ``Whole genome re-sequencing of museum specimens revels resilience to
disease in a feral population of European honey bees.'' Australian National University, Canberra, Australia, \printdate{2014-00-00}.



\ind ``Molecular signatures of ancient mutualistic coevolution in attine ants
and their fungal cultivars.'' Experimental Evolution Discussion Group, Wageningen University, Wageningen, Netherlands, \printdate{2014-00-00}.


\ind ``Whole genome re-sequencing of museum specimens revels resilience to
disease in a feral population of European honey bees.'' University of Southern California,, Los Angeles, California, United States, \printdate{2014-00-00}.


\ind ``Whole genome re-sequencing of museum specimens revels resilience to
disease in a feral population of European honey bees.'' University of Southern California,, Los Angeles, California, United States, \printdate{2014-00-00}.


\ind ``Working with degraded DNA: laboratory and bioinformatic approaches.'' University of Southern California,, Los Angeles, California, United States, \printdate{2014-00-00}.


\ind ``Development and applications of techniques to work with degraded DNA.'' Kzan' Federal University, Kazan', Russian Federation, \printdate{2013-00-00}.



\ind ``Using museum collections to understand how honey bees have survived a
disease pandemic.'' School of Life Sciences, Arizona State University, Tempe, Arizona, \printdate{2013-00-00}.


\ind ``Using museum collections to understand how honey bees have survived a
disease pandemic.'' School of Life Sciences, Arizona State University, Tempe, Arizona, \printdate{2013-00-00}.


\ind ``Using museum collections to understand how honey bees have survived a
disease pandemic.'' Integrative Biology, University of Texas, Austin, Texas, United States, \printdate{2013-00-00}.


\ind ``Using museum collections to understand how honey bees have survived a
disease pandemic.'' Neurobiology and Behavior, Cornell University, Ithaca, New York, United States, \printdate{2013-00-00}.


\ind ``Using museum collections to understand how honey bees have survived a
disease pandemic.'' CAS-MPG Partner Institute for Computational Biology, Shanghai, China, \printdate{2012-00-00}.




\ind ``Evolutionary fate of horizontally acquired genes in bdelloid rotifers.'' Ehwa Womans University, Seoul, Korea, \printdate{2013-00-00}.



\ind ``The role of adaptation and mutualistic interactions in the invasion of
an African rainforest by the little fire ant
\textit{Wasmannia auropunctata}.'' Rice University, Houston, Texas, United States, \printdate{2008-00-00}.


\ind ``The spread of an invasive ant in African lowland rainforest: effects of
environment and genetics.'' University of Hawaii, Hilo, Hawaii, United States, \printdate{2008-00-00}.


\ind ``Coevolution at the phylogenetic vs.~population-genetic scales in the
attine ant-fungal cultivar symbiosis.'' Wageningen University, Wageningen, Netherlands, \printdate{2007-00-00}.



\subsection{Invited Conference and Workshop Talks}







\ind ``Staying alive: Genetic confirmation that the Lord Howe stick insect is
not extinct.'' \emph{Genomics and collections: adaptation to macroevolution}, Canberra, Australia, \printdate{2017-06-14}.












\ind ``When subspecies collide: What can genome-wide signatures of
hybridisation tell us about speciation?.'' \emph{Australian National University, Species delimitation in the age of
genomics Workshop}, Canberra, Australia, \printdate{2015-00-00}.


























\subsection{Oral Conference Presentations}






\ind ``Staying alive: Genetic confirmation that the Lord Howe stick insect is
not extinct.'' \emph{Entomological Society of America}, Boulder, Colorado, United States, \printdate{2018-00-00}.



\ind ``Using historical collections to understand the evolutionary response of
bees to an emergent parasite.'' \emph{Society for Molecular Biology and Evolution}, Austin, Texas, United States, \printdate{2016-00-00}.




























\ind ``Transcriptional profiling of attine ant fungal symbionts.'' \emph{British Mycological Society}, Alicante, Spain, \printdate{2012-00-00}.


\ind ``Invasion of lowland rainforest by their little fire ant
\textit{Wasmannia auropunctata}.'' \emph{Department and Graduate Institute of Entomology, National Taiwan
University}, Taipei, Taiwan, \printdate{2011-00-00}.








\subsection{Poster Conference Presentations}





























\ind ``RAD-tagging and low-coverage shotgun phylogenetics with degraded DNA
from non-destructively sampled museum specimens.'' \emph{Illumina}, Phuket, Thailand, \printdate{2013-00-00}.















\subsection{Local Talks}























\ind ``Molecular signatures of ancient mutualistic coevolution in attine ants
and their fungal cultivars.'' \emph{OIST-NTU Invasive Ant Symposium, Okinawa Institute of Science and
Technology}, Okinawa, Japan, \printdate{2014-00-00}.
















\ind ``Ecology and evolution: the next synthesis.'' \emph{Sydney Brenner commemorative symposium, Okinawa Institute of Science and
Technology}, Okinawa, Japan, \printdate{2011-00-00}.






\filbreak  % may not be necessary in the future, prevents heading from being leftover
\defbibheading{publist}[\bibname]{%
  \subsection{#1}}

\begin{publications}
  \printbibrz{article}{Journal Articles}
  \printbibrz{conferences}{Conference papers \& posters}
  \printbibrz{commentary}{Commentary}
\end{publications}

\section{Service}

\subsection{Associate Dean (International), Joint Colleges of Science, Health and
Medicine, Australian National University}
\ind Indian Institute of Technology Madras Joint Degree Program steering
committee. 2019--.

\subsection{Professional Organizations}
\ind Australian Entomological Society, Education Committee member. 2018--.

\subsection{Reviewer}
\ind \textbf{Journals}: Applied Sciences, Bioinformatics, Biology Letters,
BMC Biology, BMC Evolutionary Biology, BMC Genomics, Current Opinion in
Insect Science, Ecological Research, Ecology, Ecology and Evolution,
Ecology Letters, Insectes Sociaux, Journal of Animal Ecology, Journal of
Evolutionary Biology, Journal of Visualized Experiments, Molecular
Biology and Evolution, Molecular Ecology, Molecular Ecology Resources,
Nature Ecology \& Evolution, Philosophical Transactions of the Royal
Society B: Biological Sciences, PLoS Computational Biology (Guest
Editor), PLoS Genetics, Proceedings of the Royal Society B: Biological
Sciences, Scientific Data, Scientific Reports, Toxins. 

\ind \textbf{Granting Agencies}: Australian Research Concil, Deutsche
Forschungsgemeinschaft, U.S. National Science Foundation. 


\section{Outreach}

\subsection{TV Interview}
\ind SBS News.  \href{https://www.sbs.com.au/news/australian-beekeepers-call-for-ban-on-potentially-harmful-pesticide}{Commenting on the use of neonicotinoid pesticides}. 2019-05-08

\subsection{Public talk}
\ind Japan Institute, ANU College of Asia \& the Pacific. OBJECTively - Connecting Australia and Japan: objects, cultural stories,
people, \href{http://japaninstitute.anu.edu.au/events/objectively-connecting-australia-and-japan-objects-cultural-stories-people}{Coversations: bee parasitc mites}. 2019-03-08



\end{document}
